%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://collinsmuriuki.xyz}{\Large Collins Muriuki}} & Email : \href{mailto:hello@collinsmuriuki.xyz}{hello@collinsmuriuki.xyz}\\
  \href{https://collinsmuriuki.xyz}{https://collinsmuriuki.xyz} & Mobile : +254705583540 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Flinkit GmbH}{Nairobi, Kenya}
      {Lead Full Stack Software Engineer}{August 2021 - Present}
      \resumeItemListStart
        \resumeItem{AI Generated WhatsApp Templates}
          {Developed a solution to bypass WhatsApp Business API messaging limitation through automatic generation of template messages allowing the users to send messages without any blockers}
          \resumeItem{Open API}
          {Led the development of an Open API which enabled external developers to interface with our product, resulting in more opportunities for integration into customers' systems and increased product usage.}
          \resumeItem{Salesforce Integration}
          {Implemented a bidirectional synchronization of data between Salesforce  and our client through an event driven approach via GraphQL and PostgreSQL unlocking a new avenue to attract new customers.}
          \resumeItem{Improved developer experience}
          {Addressed various technical debt through introduction of database migrations into our development and CI/ CD workflow as well as greatly improving resource provisioning through introduction of infrastructure as code via terraform. This positively improved developer experience and productivity.}
      \resumeItemListEnd
    \resumeSubheading
      {Bitfinity Network}{Nairobi, Kenya}
      {Rust Engineer}{October 2022 - January 2023}
      \resumeItemListStart
        \resumeItem{Scalable digital signature verification}
          {Developed digital signature verification tooling in Rust for Bitfinity's ethereum virtual machine. This was done by successfully abstracting the functionality in its own compute unit so that it can be scaled individually if needed.}
      \resumeItemListEnd
    \resumeSubheading
      {TIBU Health}{Nairobi, Kenya}
      {Full Stack Software Engineer}{February 2020 - August 2021}
      \resumeItemListStart
        \resumeItem{API upgrade}
          {Successfully upgraded the product to a more advanced, performant and scalable API, additionally improving scaling potential through introduction of containerization with Docker and migration to kubernetes and helm. Migrating to an upgraded API resulted in a significant reduction in latency and imroved performance in our client side application}
        \resumeItem{Real time Doctor and Patient matching algorithm}
          {Developed and deployed a real time client to doctor matching algorithm by leveraging Redis work queues and gRPC}
        \resumeItem{Development of internal observability tooling}
          {Designed and developed an internal dashboard for the medical logistics team, enabling efficient tracking and handling of medical requests made by customers on our platform. This greatly improved their productivity as they permanently migrated from use of Excel sheets}
      \resumeItemListEnd

    \resumeSubheading
      {Africa's Talking}{Nairobi, Kenya}
      {Software Engineer}{October 2020 - January 2022}
      \resumeItemListStart
        \resumeItem{Greenfield project development}
          {Successfully led the development and release of the product landing page, developer console and documentation for Africa's Talking's product, Kazzo OTP, a customer identity B2B Software as a Service.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Sqika}
      {A web platform which connects users to their favorite influencer and celebrity by allowing them to request personalized short form videos on various topics}
    \resumeSubItem{M-Pesa Rust SDK}
      {Developed an open source SDK over M-PESA, a mobile phone-based money transfer and financial services platform used in East Africa.}
    \resumeSubItem{Chatterverse}
      {A web platform that allows users to create AI generated audio conversations between famous people through their AI voices.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Rust, Python, JavaScript, Go, Elixir, SQL}
     \hfill
   }{
     \textbf{Technologies}{: AWS, React, PostgreSQL, Redis, Kubernetes, Docker, Terraform, GraphQL, gRPC}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {United States International University}{Nairobi, Kenya}
      {Bachelors in Applied Computer Technology;  GPA: 3.5/4}{January 2019}
    \resumeSubheading
      {Moringa School}{Nairobi, Kenya}
      {Certificate In Full Stack Software Development}{Aug. 2019 -- January. 2020}
  \resumeSubHeadingListEnd
\end{document}
